\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{authblk}
\geometry{margin=1in}

\title{\textbf{Tipping the Climate Equilibrium: Tensor-Based Game Theory for Identifying Critical Coalitions in Climate Policy Negotiations}}

\author[1]{Paul Schleifer\thanks{Corresponding author. Contact: paul.schleifer@hotmail.com. ORCID: \href{https://orcid.org/0009-0004-7972-3566}{0009-0004-7972-3566}}}
\affil[1]{Independent Researcher, London, United Kingdom}

\date{}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent\textbf{Manuscript type:} Full research article

\medskip
\noindent\textbf{Submission to:} Environmental and Resource Economics

\medskip
\noindent\textbf{Corresponding author:}\\
Paul Schleifer\\
Independent Researcher, London, United Kingdom\\
Email: paul.schleifer@hotmail.com

\medskip
\section*{Statements and Declarations}

\noindent\textbf{Competing interests:} The author declares no competing interests.

\medskip
\noindent\textbf{Funding:} No external funding was received for this work.

\medskip
\noindent\textbf{Data and code availability:} All analysis code and output data will be made publicly available upon acceptance. Full reproducibility instructions are included in the repository.

\medskip
\noindent\textbf{Author contribution:} Paul Schleifer is the sole author and is responsible for all aspects of the work, including conceptualisation, methodology, software, data curation, formal analysis, writing, and submission.

\medskip
\noindent\textbf{Use of AI/large language model tools:} Assistance from large language model tools was used during the preparation of this manuscript for tasks including drafting and refining prose. All intellectual content, mathematical formulations, computational results, and analytical conclusions are the sole work of the author, who takes full responsibility for the integrity of the manuscript.

\end{document}
